\chapter{The Engineering Project}
\label{chap:project}

%=================================================================================

\section{Health and Safety}

Given that the entirety of this was conducted in 

%=================================================================================

\section{Engineering Professionalism}

Using their course experience of ECOR 4995 Professional Practice, students should demonstrate how their professional responsibilities were met by the goals of their project and/or during the performance of their project. 

%=================================================================================

\section{Project Management}

One of the goals of the engineering project is real experience in working on a long-term team project.  Students should explain what project management techniques or processes were used to coordinate, manage and perform their project.

%=================================================================================

\section{Individual Contributions}

This section should carefully itemize the individual contributions of each team member. Project contributions should identify which components of work were done by each individual.  Report contributions should list the author of each major section of this report.

%---------------------------------------------------------------------------------

\subsection{Project Contributions}

Give the individual contributions of the each team member towards the project.

%---------------------------------------------------------------------------------

\subsection{Report Contributions}

Give the individual contributions of the each team member towards writing the
final report.

